Dynamic Transition Analysis with TIMES\\ I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions

### 2018-01-12 doc/poster.tex
I'm not sure we do want to investigate scenarios where decarbonization isn't the main priority

\title{\textbf{Dynamic Transition Analysis with TIMES:}\\ I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions} % Poster title

\author{Anshuman Chaube, James Stubbins, \textbf{Kathryn Huff}}
\institute{University of Illinios at Urbana-Champaign, Department of Nuclear, Plasma, and Radiological Engineering, Urbana, IL 61801}
%----------------------------------------------------------------------------------------

@@

\item Dynamic simulation of Japan's energy system in TIMES model generator using a heterogeneous model and realistic constraints will help develop near-term decarbonization strategies.

\item Policymakers will benefit from identification of high impact technologies, and creation of R\&D investment and infrastructure development timelines.

\item Simulations will quantify system sensitivity to technology readiness, and also account for secondary scenarios where decarbonization is not the main priority.

>>>>

\title{Dynamic Transition Analysis with TIMES\\ 
I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions} % Poster title

\author{\textbf{\textsc{Energy Analysis Division}}\\
        Anshuman Chaube, James Stubbins, \textbf{Kathryn Huff}}
\institute{University of Illinios at Urbana-Champaign, Department of Nuclear, Plasma, and Radiological Engineering, Urbana, IL 61801}
%----------------------------------------------------------------------------------------

@@

\item Dynamic simulation of Japan's energy system in TIMES model generator using a heterogeneous model and realistic constraints will help develop near-term decarbonization strategies.
\item Policymakers will benefit from identification of high impact technologies, and creation of R\&D investment and infrastructure development timelines.
\item Simulations will quantify system sensitivity to technology readiness.
